### 2021-10-27 README.Rmd
update README
add zenodo badge

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/bbartholdy/byoc-starch/main?urlpath=rstudio) <!-- DOI badge: [![DOI](.svg)](repo link) -->

<!-- Document structure provided by rrtools package -->

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

## Contents

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/bbartholdy/byoc-starch/main?urlpath=rstudio) 
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5604670.svg)](https://doi.org/10.5281/zenodo.5604670)

<!-- DOI badge: [![DOI](.svg)](repo link) -->

<!-- Document structure provided by rrtools package

@@

> Bartholdy, B. P. & Henry, A. G. (2021). _`r Title`_. bioRxiv <https://doi.org/xxx/xxx>

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
-->
## Contents
